\section{Introduction}
This report is a self evaluation during project "Naiad" in the course
"DVA425 - Project in Advanced Embedded Systems" at M\"{a}lardalens University.
This self evaluation looks back on weeks 15 to 20 of the project.

I'm a member of the software group.
% The report should be typeset with \LaTeX !
% The requirements that are set for the different grades are:
% \begin{description}
% \item[Grade 3] Be there and do a good job
% \item[Grade 4] Be there and take initiatives to fulfill the goals
% \item[Grade 5] Be there, take initiatives to fulfill the goals and suggest (close to research) new approaches
% \end{description}

\section{My contribution during this period}
% Started implementation with VNP...last period?...avr-ada build server.
% Implement support for at90can128 in AVR-Ada

\subsection{Documentation management}
I have led the documentation work through this period. Structuring the
overall documentation process and setting a plan for when each draft and
the final report should be finished.

\subsection{Documentation}
I've finalized my reports about "IP over CAN" and "Space plug-and-play Avionics".
During the last period I've also contributed with a new report about "Development
and Operations" which go into detail about hosting, our website, version
control system and workflows. As last note on documentation I've written
the "software architecture" part of the Sensor fusion report.

\subsection{Website scripts}
In the end of this period I've set up installation and configuration scripts
for our website so it's easy to get going in the future.

\subsection{Sensor fusion}
The sensor fusion code is not finished, it's still missing vital parts such as
the actual calculations it should make. During the last period I've structured
the Sensor fusion code into 7 different Ada tasks and added several debug print
outs. This will hopefully make it easier for those that try to work with that
code in the future.

Original Sensor fusion code is written by Per-Erik and copied from the "Mission
Control System" which has a similiar but not identical software architecture.

\section{Related work}

\subsection{Git and Github}
Continued to help other project members with Git and Github problems.

\section{Suggested grade \& motivation}
Suggested grade X. During the last period I've taken initiatives to make sure
the documentation we leave behind from this project is as good as it can be.
While writing my own reports I've been able to help others with both LaTeX and
Git questions.
