\section{Introduction}
This report is a self evaluation during project "Naiad" in the course
"DVA425 - Project in Advanced Embedded Systems" at M\"{a}lardalens University.
This self evaluation looks back on weeks 10 to 15 of the project.

I'm a member of the software group.
% The report should be typeset with \LaTeX !
% The requirements that are set for the different grades are:
% \begin{description}
% \item[Grade 3] Be there and do a good job
% \item[Grade 4] Be there and take initiatives to fulfill the goals
% \item[Grade 5] Be there, take initiatives to fulfill the goals and suggest (close to research) new approaches
% \end{description}

\section{My contribution during this period}
% Started implementation with VNP...last period?...avr-ada build server.
% Implement support for at90can128 in AVR-Ada

\subsection{Requirements list}
This period started with helping Simon mapping requirements to
design/implementation. I contributed with the template file for LibreOffice
Calc.

\subsection{Space plug-and-play Avionics and IP over CAN}
Complete drafts of respective final report are done.

\subsection{Cross-compilation of Ada against 8-bit AVR}
All code that has been written and tested on the 8-bit AVR has been written in
Windows with Adacore Libre 2012. This code has not used tagged types or
similiar advanced features in Ada. The motion control system has been
written and tested on amd64 without first checking what works on the AVR
architecture.

During this period I focused on trying to get the free and open-source
"AVR-Ada" to work on Ubuntu. This included compilation of gnu compiler
collection (gcc) 4.7 native (amd64 host) and then compiling gcc so it can cross
compile for AVR. In the end it was concluded that neither Adacore Libre 2012
nor AVR-Ada have wanted support for tagged types.

Implemented partial support for the AT90CAN128 in AVR-Ada project. This include
Timer0, Timer1 and UART1. \cite{web:sf_avr_ada}

\subsection{Reinstalled build server and Jenkins}
Reinstalled build server to compile with AVR-Ada instead of Adacore Libre.
Reinstalled jenkins and rewrote most part of the build script used.

\section{Related work}

\subsection{Design of Mission Control System}
Participated in the discussions on how to design the Mission Control System as
well as what communication should take place between Mission Control System and
Vision Systems.

\subsection{GtkAda}
I helped out trying to get GtkAda to work. Tested out different versions from
Debian package library and Adacore.

\subsection{Git and Github}
Continued to help other project members with Git and Github problems.

\subsection{XML parser}
Started work on a XML parser and validator to be able to transform missions
defined in XML to code that our virtual machine will understand.

\section{Suggested grade \& motivation}
Suggested grade X. This period I've showed up and taken initiative to several
parts such as structure for the requirements list to fixing AVR-Ada for the
AT90CAN128.
